# Exploration

```{r, child="_common.Rmd"}
```

<p style="font-weight:bold; color:red;">INCOMPLETE DRAFT</p>

> ...

```{block, type="rmdkey"}
In this chapter you will learn:

- the goals of this textbook
- the reasoning for using the R programming language
- important text conventions employed in this textbook
```

<!-- COURSE STRUCTURE

TUTORIALS:

- ...

SWIRL:

- ...

WORKED/ RECIPE:

- ...

PROJECT:

- ...

GOALS:

...

-->

## ...

Idea....

Get [Meditations by Marcus Aurelius](https://en.wikipedia.org/wiki/Meditations) from `gutenbergr` (`gutenberg_id == 2680`). 

- The 12 books are not believed to be in chronological order. It may be interesting to look at whether there is some book-level similarities/ differences that might suggest that some books are more similar than others. 
- A sentiment analysis would be interesting as well --do the books show similar/ different patterns in terms of sentiment?
- Topic modeling to uncover themes in the books?

### Packages {#exploration-packages}

```{r acquire-data-packages}
# Packages
# pacman::p_load(quanteda)
```
